\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\begin{flushleft}
\centering{\huge\textbf{Amit Agrwal}
\\{\newline\small2nd Year Undergraduate, B.Tech (IT)}}
\end{flushleft}
\\\textbf{LinkedIn : }{\href https://www.linkedin.com/in/abhigya02/} \hfill\textbf{Email : }abhigyaverma27@gmail.com
\\\textbf{Github : }https://github.com/abhi27-web \hfill\textbf{Phone : }+91-883908494
\vspace{-6pt}
\\
\noindent\rule[0.5ex]{\linewidth}{1pt}
{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{6.0cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CGPA/$\%$}\\
\hline
\centering{2019} - 2023 & \centering{B.Tech} & \centering{Indira Gandhi Delhi Technical University for Women} & 8.36/10\\
\hline
\end{tabular}
\end{center}

{\large \textbf{\begin{tcolorbox}\textsc{Internship Experience}\end{tcolorbox}}}
\begin{itemize}
\item \textbf {\underline{Summer Intern, ML and Data Science, ACM IGDTUW}}\hfill\hfill(\textit{June 2020 - July 2020})
\begin{itemize}
\item Built a talking chat bot in Python using Data Collection, Text pre-processing, Vectorization and metric analysis.
\item Chat bot gave information related to COVID-19 pandemic, \&
helped people to overcome anxiety, depression and stress.
\end{itemize}

\item \textbf {\underline{Teaching Assistant, Summer Workshop, ACM IGDTUW}}\hfill\hfill(\textit{June 2021 - July 2021})
\begin{itemize}
\item Worked as a teaching assistant in summer workshop on Computational Approaches for Social Good.
\item Helped in building assignments, worked as a mentor in projects and graded assignments based on the given parameters.
\end{itemize}
\end{itemize}

{\large \textbf{\begin{tcolorbox}\textsc{Key Projects}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Snake Game- } {\underline{\href{http://bit.ly/3jmlcPe}}}
\begin{itemize}
\item Built a game in \textbf{javascript} and used the data structure, \textbf{array} to track the movement of snake.
\end{itemize}

\item \textbf{Aveksha- } {\underline{\href{https://aveksha.herokuapp.com/stats}}}
\begin{itemize}
\item Scraped out women related location specific
tweets using \textbf{python module tweepy} and analyzed their \textbf{sentiments}.
\item Identified top hate speech users of the selected location by segregating tweets as negative, positive, and neutral using \textbf{Text blob} library of python
\end{itemize}
\item \textbf{I-Care MedicalBot- } {\underline{\href{https://bit.ly/3wNNJmt}}}
\begin{itemize}
\item Built a talking audio chat bot using \textbf{Python} that talks about COVID 19.
\item Average cosine similarity between the user questions and Bot response as \textbf{47.5 percent}.
\end{itemize}
\end{itemize}
\vspace{-2mm}

{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\itemsep0em
\item \textbf{Programming Languages and stacks: }C++, Data Analytics, Python, Machine Learning, CS Fundamentals
\item \textbf{Coursework: } Data Structures, Database Management Systems (DBMS), Software Engineering, Computer Organization and Architecture, Operating System, Design and Analysis of Algorithm, Object Oriented Programming, Operations Management
\end{itemize}
\medskip

{\large \textbf{\begin{tcolorbox}\textsc{Achievements}\end{tcolorbox}}}
\begin{itemize}
\item Selected for \textbf{Microsoft Engage '21}
\item Rated \textbf{1626} highest at CodeChef(3 stars)
\item Global Rank of \textbf{439} in the January Long           Challenge 2021 Division 3 at CodeChef and Ranked \textbf{3rd} in the University.
\item \textbf{3 Star Badge} for C++ on HackerRank
\item \textbf{Runner Up} in \textbf{Global Hackathon- Rotathon} in the theme \textbf{Women Security}.
\item \textbf{2nd Runner Up} - STEMathon conducted by ACM IGDTUW under Advaya 2.0
\item Selected in the \textbf{top 20} out of \textbf{500+} teams in National Level Hackathon and selected for research work by mentors.
\item \textbf{First Prize} in the Ninja Wave 2.0 at Indira Gandhi Delhi Technical University for Women.
\item Participated in NCERT Science Exhibitions number of times and represented school at Regional Level in 2018, 2015 \& 2013.
\end{itemize}
\medskip
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize}

{\large \textbf {\begin{tcolorbox}\textsc{Leadership Positions}\end{tcolorbox}}}
\begin{itemize}
\item \textbf {\underline{Microsoft Learn Student Ambassador- Beta
}}\hfill\hfill(\textit{April 2021 - Present})
\begin{itemize}
\item Conducting workshop series for \textbf{50+ mentees} teaching technical stack \textbf{Machine learning} using \textbf{Python}.
\end{itemize}
\item \textbf {\underline{Campus Ambassador, Cisco}}\hfill\hfill(\textit{March 2021 - Present})
\begin{itemize}
\item Acted as a \textbf{brand ambassador} for Cisco to create brand awareness for students.
\end{itemize}
\item \textbf {\underline{Executive Lead- Public Relation
ACM, IGDTUW}}\hfill\hfill(\textit{Jan 2021 - Present})
\begin{itemize}
\item Collaborating with \textbf{ACM student chapters} and conducting
sessions and programming contests with them.
\item Conducted tech week \textbf{Advyaya} with a number of exciting
speakers, events and competitions.
\end{itemize}
%\item Acted as a link between Placement core team, companies and Students during placement process.
\item \textbf {\underline{Project Coordinator, ML Circle, 
Google Developer’s Student Club, IGDTUW}}\hfill\hfill(\textit{Sep 2020 - Present})
\begin{itemize}
\item Speaker in Session- \textbf{Introduction to ML} for \textbf{100+ members}.
\item Leading a team of \textbf{8 members} building a \textbf{Deep Learning} project.
\end{itemize}

\item \textbf {\underline{Core Member, Peer Education and Life Skills Society INSTINCT, IGDTUW}}\hfill\hfill(\textit{Jan 2020 - Present})
\begin{itemize}
\item Organized sessions on topics like Mental Health, Road map
for sophomores, Scholarships, etc. to help peers in all-round
development.
\item Conducted activities like stress buster, group discussions, debates etc. to help in de-stressing
\end{itemize}
\vspace{1mm}
\end{itemize}

\end{document}
